The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-10-01 paper2_JNLS/paper.tex
NM

Our particular focus is the laboratory experiments of Bolles et al.~\cite{bolles2019anomalous}, who demonstrated the emergence of anomalous statistics from a randomized wave-field encountering an abrupt depth change (ADC). In these experiments, the incoming wave-field is generated with nearly Gaussian statistics, and a plexiglass step placed near the middle of the tank creates the depth change. Upon passing into the region of shallower depth, the wave distribution skews markedly, with deviation from Gaussian being most pronounced a short distance downstream of the ADC. Inspired by these experimental observations, Majda et al.~\cite{majda2019statistical} developed a theoretical foundation that accurately captures several aspects of the anomalous behavior. The theory is based on deterministic and statistical analysis of the truncated Korteweg–de Vries (TKdV) equations, and uses a combination of computational, statistical, and analytical tools. In follow-up work, Majda and Qi \cite{majdaqi2019} analyzed more severely truncated, lower-dimensional systems that were shown to exhibit many of the same anomalous properties while enjoying a more tractable structure.

@@

>>>>

Our particular focus is the laboratory experiments of Bolles et al.~\cite{bolles2019anomalous}, who demonstrated the emergence of anomalous statistics from a randomized wave-field encountering an abrupt depth change (ADC). In these experiments, the incoming wave-field is generated with nearly Gaussian statistics, and a plexiglass step placed near the middle of the tank creates the depth change. Upon passing into the region of shallower depth, the wave distribution skews strongly towards positive displacement, with deviation from Gaussian being most pronounced a short distance downstream of the ADC. Inspired by these experimental observations, Majda et al.~\cite{majda2019statistical} developed a theoretical foundation that accurately captures several key aspects of the anomalous behavior. The theory is based on deterministic and statistical analysis of the truncated Korteweg–de Vries (TKdV) equations, and uses a combination of computational, statistical, and analytical tools. In follow-up work, Majda and Qi \cite{majdaqi2019} analyzed more severely truncated, lower-dimensional systems that were shown to exhibit many of the same anomalous properties while enjoying a more tractable structure.

@@

Show diagram, talk about different statistics on either side of ADC. Say Bolles found the downstream measurements to be remarkably well fit by a mean-zero gamma distribution.
